A Technique for Inter-Catalogue Recommendations

### 2014-06-10 paper2/paper.tex
Finished re-working Experiment section and added Evaluation section.

@@

To evaluate our inter-retailer recommendation methods, we simulate the problem
by randomly partitioning Macy's products into two disjoint sets. Given the
original recommendation graph, each partition therefore corresponds to a graph
cut. Our premise is that an ideal recommendation method could guess the edges in
this cut with high precision and recall.

Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms.  Together, these metrics capture how effective one is at
guessing items within a target set. Consider a typical Macy's category, for
example, Dresses, which contains approximately $3,500$ items. Randomly 
partitioning results in two sets, each with about $1,750$ items. For each 
interset recommendation, we must therefore choose two nodes, one from each of the two
sets. That is, we have $1,750 \times 1,750 > 3 \times 10^6$ choices. Choosing
the correct edges is a formidable challenge to say the least. It is therefore
worth asking: Are some prediction errors better or worse than others? The graph
nature of our problem reveals that the answer is yes. It is better to guess an
edge that connects two items that are separated by two edges in the original
graph than to connect two items that are separated by five edges. We therefore
introduce the notion of {\em 2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ are
defined as

@@

In these experiments, we perform the partitioning on a per-category basis.

Next, for each category (e.g. Women Activewear, Men Dress Shirts, etc.), we
partition the products into two disjoint sets to simulate the catalogues of two
distinct retailers. Importantly, we ensure that the items of each brand are
entirely within a single partition. In this way, we preclude the easiest method
of associating two items: recongnizing a common brand. This is done to increase
the difficulty and realism of our experiment.

To make this partition realistic, we
ensure that no brand has products in both catalogue. We remove all
recommendations between products from one partition to the other, thus creating
two entirely disjoint and unconnected catalogues.

Now, we can use this partition to test a method for constructing recommendation.
For each product in each of the two catalogues, we use our recommender to choose
which products to recommend in the other catalogue. To make this problem
slightly simpler, we restrict recommendations to be within the same category,
such as Women's Dresses or Men's Shoes. In this way, connecting up entire
catalogues becomes a series of smaller tasks of connecting the products in each
category.

For this experiment, we have access to all of the true inter-catalogue
recommendations from the unpartitioned Macy's catalogue. Although we don't use
this information for constructing recommendations between the partitioned
graphs, we can use the original recommendations as a gold-standard to test the
construct ones. Using these gold-standard recommendations, we can evaluate the
precision and recall of the predicted inter-catalogue recommendations.

For the Macy's catalogue, each product has four recommendations. This means that
on average, there are only two gold-standard inter-catalogue recommendations
from each product. Since there potentially are other good
recommendations besides these two, we create another metric that expands our
notion of a correct recommendation. Here we extend the definition of a good
connection to include recommendations of recommendations in the original
catalgoue. For example, if Product B is recommended for Product A and 
Product C is recommended for Product B, we say that Product C is still a good 
recommendation for Product A. This leads us to the notions of 2-precision and 
2-recall.

For a rigorous definition of 2-precision and 2-recall, we first propose the idea
of a recommender graph. A recommender graph has products as nodes and
recommendations as edges. If Product B is recommended for Product A, there is an
edge between node A and node B in the graph. For simplicity, we define our
recommender graphs to be undirected, but we note that they could be interpreted
as directed graphs as well. With this terminology, our problem becomes one of
connecting two disjoint recommender graphs by adding edges between them.

2-precision is defined as the percentage of predicted edges that are within two
steps in the original, unpartitioned recommender graph. In the example above,
Product A and Product C are within two steps in the original graph, thus an edge
between A and C is considered correct and increases precision. 2-recall is
defined analogously. Here, we consider the new recommender graph, consisting of
the two partitioned recommender graphs connected by the predicted
recommendations. 2-recall is then the percentage of gold-standard edges that 
are within two steps in the predicted recommender graph.

@@

>>>>

To simplify the present study, we transform these directed recommendation graphs
into undirected graphs. This is consistently done using the following policy:
For each pair of items connected by a single directed edge, replace this edge
with a single undirected edge. For each pair of items connected by two
oppositely directed edges, replace both edges with a single undirected edge.
Working with undirected graphs simplifies both the prediction algorithms as well
as the evaluation of their performance. At the same time, by ignoring the
directionality of the original edges, we are discarding important information.
It would therefore be worthwhile to consider the more difficult problem of
connecting directed recommendation graphs in a future study.

@@

To evaluate our inter-retailer recommendation methods, we simulate the problem
by randomly partitioning Macy's products into two disjoint sets. Given the
original recommendation graph, each partition therefore corresponds to a graph
cut. The edges in this graph cut form a {\em gold-standard} since it is assumed
that these are indeed ``good'' recommendations. Our premise is that an ideal
recommendation method could guess these gold-standard edges with high precision
and recall.

For each experiment, we choose a particular category from the Macy's catalogue
(e.g. Women Activewear, Men Dress Shirts, etc.). Since most recommendations are
between items in a common category, very few, though some, edges are lost by
confining ourselves to an individual category. Edges that are lost in this way
do not participate in the experiment and are not considered during evaluation.
Also, we randomly partition the items in the category such that all items
associated with a particular brand are entirely within a single partition. In
this way, we preclude the easiest method of associating two items: recognizing
a common brand. This is done to increase the difficulty and realism of the
experiments.

Having partitioned the graph of items, we now predict recommendation relations
between items across the partitions. Each prediction algorithm has knowledge of
all items in each partition, including their descriptions and all
recommendations (i.e.  edges) between items in a common partition. In addition,
the algorithms may exploit the fact that most items listed at www.macys.com are
accompanied by four recommended items. The algorithms do not have knowledge of
the recommendations (i.e. edges) between items across partitions. Each
prediction algorithm is then free to choose an arbitrary number of edges as long
as 1) the items connected by the predicted edge are not in the same partition
and 2) at most one edge is predicted for a particular pair of items.

\section*{Evaluation}
Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms \cite{Powers2011}. Together, these metrics capture how
effective one is at guessing items within a target set. Consider a typical
Macy's category, for example, Dresses, which contains approximately $3,500$
items. Suppose that randomly partitioning results in two sets, each with about
$1,750$ items. For each interset recommendation, we must therefore choose two
nodes, one from each of the two sets. That is, we have $1,750 \times 1,750 > 3
\times 10^6$ choices. Choosing the correct edges is a formidable challenge to
say the least. It is therefore worth asking: Are some prediction errors better
or worse than others?

The graph nature of our problem reveals that the answer to this question is
yes. For instance, it is better to guess an edge that connects two items that
are separated by two edges in the original graph than to connect two items that
are separated by five edges. We therefore introduce the notion of {\em
2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ are defined as

@@

The following definitions will prove helpful. Let $G$ be the original
unpartitioned graph formed from the partitions together with the lost edges $L$
and let $G^{\prime}$ be the new graph formed from the partitions together with
the predicted edges $P$.  In the context of {\em 2-precision}, an edge in $P$
that connects items $A$ and $B$ is considered correct if 1) $A$ and $B$ share an
edge within $G$ or 2) $A$ shares an edge with a direct neighbor of $B$ within
$G$ or 3) a direct neighbor of $A$ shares an edge with $B$ within $G$.
Meanwhile, in the context of {\em 2-recall}, an edge in $L$ that connects items
$C$ and $D$ is considered recalled if 1) $C$ and $D$ share an edge within
$G^{\prime}$ or 2) $C$ shares an edge with a direct neighbor of $D$ within
$G^{\prime}$ or 3) a direct neighbor of $C$ shares an edge with $D$ within
$G^{\prime}$.

We use both traditional precision, recall, and $F_1$ score as well as {\em
2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ score to evaluate our prediction
algorithms. Including the latter set of metrics provides a more complete picture
of algorithmic performance. These additional metrics also accommodate the fact
that the edges of $G$ do not necessarily correspond to the only or even the best
item-item recommendations. We therefore suggest that while traditional precision
and recall are relevant metrics, relative performance as measured by {\em
2-precision} and {\em 2-recall} better captures the effectiveness of these
prediction algorithms.

@@

\bibitem{Powers2011}
    Powers, David M W.
    ``Evaluation: From Precision, Recall and F-Measure to ROC, Informedness,
Markedness \& Correlation.''
    \emph{Journal of Machine Learning Technologies} \textbf{2}, 37-63, 2011.
